% ******************
%  Copyright 2024 TekFive, Inc. and contributors
%
%   Licensed under the Apache License, Version 2.0 (the "License");
%   you may not use this file except in compliance with the License.
%   You may obtain a copy of the License at
%
%     http://www.apache.org/licenses/LICENSE-2.0
%
%   Unless required by applicable law or agreed to in writing, software
%   distributed under the License is distributed on an "AS IS" BASIS,
%   WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
%   See the License for the specific language governing permissions and
%   limitations under the License.
% ******************

\RequirePackage{snapshot}
\documentclass[10pt,twoside]{article}
\usepackage[sided=twoside]{tekfive}
\usepackage{float}
\usepackage{caption}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{tabulary}
\usepackage[scaled]{helvet}
\usepackage[absolute]{textpos}
\usepackage[left]{lineno}
\usepackage[yyyymmdd,hhmmss]{datetime}
\usepackage{comment}
\usepackage{xparse}
\usepackage{ifpdf}
\usepackage{catchfile}

\newcommand{\getenv}[3][]{%
  \CatchFileEdef{\temp}{"|kpsewhich --var-value #2"}{\endlinechar=-1}%
  \typeout{\temp}%
  \ifx\temp\empty\def\temp{#3}\fi%
  \if\relax\detokenize{#1}\relax\temp\else\let#1\temp\fi}

\renewcommand*\familydefault{\sfdefault}

\newenvironment{ppl}{\fontfamily{ppl}\selectfont\itshape}{\par}

\renewcommand{\abstractname}{Executive Summary}

\newcommand{\projectName}{\emph{AutonomousTrust }}
%\newcommand{\analysisName}{\emph{Flexline }}
\newcommand{\analysisName}{\emph{MaterialCentral }}

\bibliographystyle{unsrt}

\title{\textbf{\huge \projectName}\\ High-trust systems for secure cooperation}
\author{Sean M. Brennan}
\date{\monthname{} \the\year}

\getenv[\SCENARIO]{AUTONOMOUSTRUST_SCENARIO}{dod}%\show\SCENARIO


\begin{document}

\ifpdf
\TekFiveTitle
\else
\chapter{\projectName}
\fi

\begin{abstract}
	Cybersecurity efforts are woefully struggling due to the utterly non-scalable assumptions currently embedded in our computing paradigms.
	Software, hardware and administrative strategies, too numerous to count, all attempt to shoehorn security into new and existing systems, only to impair automated cooperation and collaboration.
	We struggle with this because default human models of reciprocity simply do not hold at large scales, or when participants are at cross-purposes.
	Our software constructs unconsciously reflect that.
	
	We should not have to think about security; automation should take care of that for us.
	Why doesn't it?
	Because we haven't taught computers how to trust.
	To combat this limitation we allow the machine to be in charge of the trust model - and that in turn unlocks more efficient processing (less noise), more direct routing (no middleman), and as such much greater scaling, securely.
		
	The ecosystem we present here is fully realizable with current technology --- no special hardware (though we might be careful about what we choose), no unproven libraries (but again choosing carefully) --- just small messages over any connection and a few small, shared blockchain ledgers.
\end{abstract}

\section{Introduction}\label{sec:intro}
\input{introduction}

\section{Background}\label{sec:background}
\input{background}

\section{Implementation}\label{sec:implementation}
\input{implementation}

\section{Security}\label{sec:vectors}
\input{security}

\section{Conclusion}\label{sec:conclusion}

\projectName represents a new paradigm in computing wherein security is \underline{primary}.
Combining the best of cryptography, blockchain, and distributed computing technologies, this system creates a setting for automated software agents to interact and self-regulate as a community.
When combined with TekFive's \analysisName product and program-correctness expertise, \projectName offers a comprehensive environment for decentralized computing that minimizes security risks and optimizes cooperation.
\\[10pt]
\input{\SCENARIO/scenario_conclusion}

Our security approach holds for more everyday circumstances as well.
Given what we know about the SunBurst supply-chain attack, \projectName would have eliminated the routes this hack took for both the vendor and their clients.
In this case, the protection is primarily due to the automatic capabilities restrictions that arise naturally in \projectName.
\\[10pt]
One glaring omission we have not addressed here is the potential vulnerabilities presented by the operating system and hardware that \projectName runs on.
The equally obvious solution would be to run our system on bare metal, or a minimal, provably-secure OS. This will be the subject of additional research.

\nocite{*}

\bibliography{HighTrust}

\end{document}
